Speed estimation for vehicles using \\SVM classification and edge detection

### 2016-06-15 Administratie/report/paper.tex
Paper classifier results

\subsection{SVM classification}\label{results-svm-classification}
We iterated through several parameter values (as discussed in \ref{parameters-classification}) to find optimal classification for road detection. For each combination of parameters we train and test on different combinations of datasets. For each combination we calculate the F-scores. These scores are used to compare the classification results (higher F-scores indicate better classification).

Different combinations of training sets were selected of the four given datasets (training sets are each time shown on the x-axis on the graphs). The trained classifier is then tested on the remaining datasets.

\subsubsection{Kernels}
As previously mentioned in section \ref{methods-kernels}, there are two SVM kernels we can use for this classification problem. On average, we tend to get a nearly 11\% increase in F-scores using RBF kernel instead of linear kernel. It is safe to say the RBF kernel outperforms the linear kernel for this classification problem in all of our test scenarios.

\subsubsection{Block size}
In general, block sizes 16x16px and 32x32px tend to show the better results. As an example we present the F-scores for LBP and color with road marks in figure \ref{fig:lbp-col-wi-rm}. Other combinations follow the same trend. For the goal of this application, a smaller block size will be more practical (i.e. better accuracy). This is why we prefer the block size of 16x16px.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/RBF_LBP_Col_wi_RM.png}
\caption{F-scores for LBP and color with road marks using RBF kernel}
\label{fig:lbp-col-wi-rm}
\end{figure}

>>>>

\subsection{SVM classification}\label{results-svm-classification}
We iterated through several parameter values (as discussed in \ref{parameters-classification}) to find optimal classification for road detection. For each combination of parameters we train and test on different combinations of datasets. For each combination we calculate the F1-scores \cite. These scores are used to compare the classification results (higher F-scores indicate better classification).

Different combinations of training sets were selected of the four given datasets (training sets used are each time shown on the x-axis on the graphs). The trained classifier is then tested on the remaining datasets.

\subsubsection{Kernels}
As previously mentioned in section \ref{methods-kernels}, there are two SVM kernels we can use for this classification problem. On average, we tend to get a nearly 10\% increase in F-scores using an RBF kernel instead of a linear kernel. It is safe to say the RBF kernel outperforms the linear kernel for this classification problem in all of our test scenarios.

\subsubsection{Block size}
In general, block sizes 16x16px and 32x32px tend to show the better results. As an example we present the F-scores for using color feature vectors with road marks in figure \ref{fig:col-wi-rm}. Other combinations follow the same trend, although 32x32px sometimes performs slightly better. For the goal of this application, a smaller block size will be more practical (i.e. better accuracy). This is why we prefer the block size of 16x16px.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{fig/RBF_Col_wi_RM.png}
\caption{F-scores for color with road marks using RBF kernel}
\label{fig:col-wi-rm}
\end{figure}
